Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2020-09-10 ehp_revision/writing/ehp_response_darlings.tex
Work some more on revisions

>>>>

# R2 Comment 1

A tropical cyclone brings a number of physical hazards, including the four 
included in our study---wind, rain, flooding, and tornadoes. These separate 
hazards may each cause health impacts and in some cases might act together 
in synergy in elevating health risks. For example, severe wind and rain 
together might create a higher probability of power outages, since the rain 
could soften the ground and make it more likely that the wind can uproot 
trees. These physical hazards tend to follow different patterns, and this is
something that's intuitively understood by atmospheric scientists who study 
the storms. Storm winds tend to decrease rapidly once a storm's center is 
over land, for example, because the storm loses its main energy source---warm
water. Rainfall can persist, and might be particularly severe when the storm 
hits landscape that is not smooth, like the Appalachian Mountains. Tornadoes
can be generated in outer bands of the storm, far from the storm's center, 
but this tends to only happen in the southern half of the US. Rain and flooding
will sometimes align spatially, but you can also have severe flooding downstream
from the area that receives the most severe rain, particularly in coastal areas
with large networks of waterways.

None of these patterns would be particularly surprising to an atmospheric scientist, 
but many epidemiologists might not be aware of them, or of how they play into
exposure assessment for tropical cyclone epidemiology. Many environmental 
epidemiologists have a training that was focused more on epidemiology and 
biostatistics and rely on collaborations with experts in engineering,
atmospheric science, or environmental health to ensure that they understand
and are appropriately applying exposure assessment. In the case of tropical 
cyclones, it is clear that they generate a mixture of physical hazards. 
There has been a lot of methodological development and thought recently in 
environmental epidemiology about how to study mixtures of chemicals---for example, 
the mixture of air pollutants that a person might be exposed to, rather than 
studying the individual effects of single air pollutants. 
These mixture methods require an understanding of how the different components
are associated with each other. In the case of binary, rather than continuous,
exposure, this will be expressed as agreement among the different exposures.

First, if exposure to a pair of different hazards strongly agrees (i.e., when a
county is exposed to one hazard, they are typically also exposed to a second),
this would have several implications for epidemiological research, especially
for multi-year studies:

- From a statistical modeling point of view, if you tried to include each hazard
as a separate independent variable, you would run into problems with
collinearity if fitting the study data with a generalized linear model or other
regression model. One implication of this is that the confidence intervals on
effect estimates for the two variables would be inflated, potentially a lot,
because the model would struggle to figure out which of the two variables the
weight should be placed on, and so this uncertainty would be reflected in the
size of the associated confidence intervals.
- If you see an effect, it would be very hard to try to determine if the causal
pathway goes through the first hazard or the second. To mitigate effects, it is
important to understand the pathway through which they happen, and it might be
easier to get clues towards pathways if the hazards are better separated. By
analogy, if you were able to conduct a controlled experiment to look at the
effects of each hazard, jointly and in combination, you would design separation
in the assignment of these treatments, so you could distinguish between the two
factors. For tropical cyclone epidemiology, we are limited to an observational
analysis, but the area of causal inference is doing a lot to explore how we can
design observational studies and analyze data to come closer to what we might be
able to see with a randomized control study. To determine which of those methods
could be used for tropical cyclone epidemiology, it is important to understand
the interplay of these patterns of exposures.
- If this is the case, and a study is conducted on a single hazard of the storm, 
then there is the risk that results have been confounded by a different hazard
of the storm. 
- On the positive side, in this case the researcher may be able to fit a simpler
statistical model to estimate the joint effects of exposure to the storm as a
whole. Statistical models of mixtures can be complex to lay out, and their 
results can be hard to interpret and explain to others. If all hazards of a 
tropical cyclone follow very similar spatial patterns, then it would be 
reasonable to model tropical cyclone exposure based on one of the hazards
(and it agreement is strong enough, it wouldn't make much difference which 
of the hazards was used for this). This would allow for the use of very 
straightforward statistical modeling, drawing on well-developed models currently
used in environmental epidemiology to study things like the health risk associated
with exposure to a single pollutant or a single physical hazard like outdoor 
temperature.

Second, if a pair of hazards tend to have little spatial overlap among 
counties, this also brings some implications for epidemiological study design
and statistical analysis:

- In this case, a single-hazard analysis could miss a lot of the risk created
by the storm as a whole. This is a concern because there have been some cases
of studies that have assessed exposure based on a single storm, typically wind.
[Grabich example, Darren Sun example]. We are aware of one other paper 
currently under review that takes this same approach of focusing on the wind
hazard of these storms. .... In interpreting these papers, it is helpful to
know if this hazard can stand as a reasonable proxy to the collection of 
physical hazards of the storm. If not, the paper must be interpreted as 
investigating

In the past, much of tropical cyclone epidemiology focused on cases studies of
single storms. Multi-year studies are becoming more common. Both types of
studies are important in exploring both typical and unusual health risks that
can be caused by these storms. Therefore, it's important to understand the
patterns between these different hazards both for single storms and across many
storms. In our analysis, we find that these hazards typically are not in strong
agreement across most storms, suggesting that mixture methods could be
meaningfully applied in most cases, and that there may often be the chance to
separate the role of different hazards through such models. However, we also
find that there are a few storms for which the hazards follow very similar
spatial patterns (Hurricane Floyd in 1999, for example), and in these cases
there may be problems of multi-collinearity and non-separability of different
hazard effects if a researcher tries to fit a model that incorporates each
separate hazard.

Issues:

1. **Interpretation** Effect of one hazard, or storm as a whole?

2. **Confounding**

3. **Multi-collinearity**

4. **Disentangling role of different hazards**

5. **Statistical power** (to separate effects of different hazards)

------------------------------------------------------------------------------

2. These results will not be surprising to an atmospheric scientist / disaster
researcher, but there are environmental epidemiologists who have done research
on other exposures and are now starting to study tropical cyclones (session at
ISEE, for example). It is useful for epidemiologists entering into tropical
cyclone research to understand these facets of tropical cyclone exposure,
including the distinction between the very coastal wind exposures and other
hazards that tend to reach further inland.
3. There are epidemiological studies that have used only one hazard for exposure
assessment. This has most often been the case for wind. If this exposure
assessment is meant to capture "tropical cyclone exposure" in general, with all
the hazards that are related to tropical cyclones, then there is the chance for
exposure misclassification if this single hazard is used.
4. In the past, it was a very complex issue to try to pull together data on all
these hazards. We agree that now that we have provided a dataset with all of
them, epidemiologists should be thinking about multi-hazard analyses. However,
there still will be some barriers to that. [Recent work on multi-pollutant
exposures and the complexities associated with that.] If one of the hazards
dominates in explaining associated health risk, then in some cases it might be
reasonable to focus on that hazard, but in that case it is critical, based on
our results, to remember that the exposure assessment is not capturing all
hazards of the storms.

The largest-scale county-level exposure study is likely that of @zandbergen2009,
which estimated exposure in US counties to all US landfalling Atlantic basin
tropical storms between 1851 and 2003, using both distance and an exposure
metric that incorporated distance and windspeed. They used this exposure
evaluation to create maps of total exposure to tropical storms within US
counties, as well as to explore associations between a county's long-term
exposure to tropical storms and its location, distance from the coast, size, and
shape [@zandbergen2009]. @kruk2010 explored exposure to hurricane-related winds
in the United States, including inland areas, for 1900-2008.

Geographical patterns can differ for these different
storm hazards, and so exposure assessment based on one hazard could create
exposure misclassification if the pathway for health risks is through a
different storm hazard.

A tropical cyclone's high winds can bring health risks and property damage
through structural damage of houses and other buildings, falling trees, and
wind-borne debris [@rappaport2000] and cause power
outages [@liu2005; han2009], which introduce a number of threats to
human and ecological health, including water quality risks if the outage affects
wastewater treatment plants [@mallin2006].  Other risks can exist
without severe wind; for example, one study found that most of the direct
hurricane-related deaths in the US between 1970 and 1999 occurred in cases
when wind was below hurricane strength, including for Tropical Storms Charley
in 1998 and Alberto in 1994 [@rappaport2000].  Tropical cyclones can
produce excessive rain, especially in certain topographies (e.g., near
mountains), so counties well inland sometimes experience more extreme rain than
coastal counties. Flood risks from tropical cyclones can result from this rain,
although the two risks are not perfectly correlated [@chen2015]. In the
US, over half of hurricane-related direct deaths from 1970 to 1999 from
Atlantic basin storms were a result of freshwater
flooding [@rappaport2000]. Flooding can also degrade water
quality [@mallin2006], which can threaten both human and ecological
health.

If a study misclassifies exposure to the hazard or hazards that cause the
health risk being studied, the study will generate biased estimates of tropical
cyclone risks and impacts. Further, when different studies use different
methods to assess exposure to tropical cyclones, their results are difficult to
meaningfully compare and aggregate. If different methods identify
similar sets of communities as ``exposed'',  these concerns are less serious.
However, if different methods differ substantially in which communities they
identify as ``exposed'', it makes it very important that epidemiological
studies are thoughtful in how they assess exposure.

These analyses can also help researchers compare and interpret results from
previous epidemiological studies that have assessed tropical cyclone exposure in
different ways, helping to [synthesize] previous epidemiologic results to form a
better picture of how these storms can affect human health.

However, these frequency maps, together with evidence from
specific tropical cyclones (Figures \ref{fig:ivanexposure}
and \ref{fig:jaccard}),  do illustrate the potential for strong differences in
spatial patterns in tropical cyclone exposures, depending on which tropical
cyclone hazards are considered.  A few previous studies have sought to
determine county-level exposure to tropical cyclones over multi-year periods,
including @zandbergen2009, which estimated exposure in US
counties to all US landfalling Atlantic-basin tropical cyclones
between 1851 and 2003, using both a distance-based metric and a metric that
combined distance and windspeed, and [@kruk2010], which explored
exposure to hurricane-related winds in the US, including inland areas,
for 1900--2008.  Our results suggest that such exposure assessments may
perform well in capturing some tropical cyclone hazards (e.g., wind), but
likely miss other potentially dangerous tropical cyclone exposures, especially
for hazards that repeatedly threaten northern or inland counties (e.g., rain,
flooding).

Therefore, use of distance to assess tropical cyclone exposure for impact
studies could result in problematic exposure misclassification, which could mask
true associations, even strong associations, between tropical cyclone exposure
and outcomes of interest in impact studies [@savitz2016interpreting;
armstrong1998effect]. The use of a single hazard-based metric (e.g., wind) could
cause similar problems if the impact is driven, at least in part, by a different
hazard or by multiple hazards of the tropical cyclone.

If measurements of one storm hazard are used as a proxy to capture exposure to
a different hazard, or a non-hazard proxy like distance to the storm track is
used to assess exposure to storm hazards, the resulting exposure
misclassification could be differential (i.e., associated with the outcome of
interest or with factors associated with risk of the outcome of interest).

Therefore for most tropical cyclones, since exposure assessments often differ
across storm hazards, as well as between each storm hazard and a distance-based
proxy measurement, exposure misclassification is a potential risk.

Further, we investigated agreement in exposure assessment across these metrics
when applied individually. We found large differences in which counties are
exposed to different hazards of tropical cyclones and that distance is, at
best, a moderate, and often a very poor, surrogate for exposure to the specific
tropical cyclone hazards of high wind, extreme rainfall, flooding, and
tornadoes. Use of distance as a surrogate for any of these hazards, or exposure
assessment based on one hazard when the pathway for health impacts is in part
or full through another storm hazard, could lead to exposure misclassification.
In the case of tropical cyclone risk and impact studies, including
epidemiological studies, this would result in biased estimates.  Our findings
highlight the importance of clarifying the potential pathway from tropical
cyclone hazards to health impacts when conducting tropical cyclone
epidemiological studies, and then basing exposure assessment on these hazards.

---------------------------------------------------------------------------

It is obvious that it is typically better, but in cases where the proxy is much
more practical to measure, it may need to be more than just a bit better, but
instead substantially better. Also, there could be some cases where the proxy
might actually be better---for example, if the proxy can be measured with very
low level, while the direct exposure measure might only be measurable with high
error. In that case, the proxy could be the better metric and might provide a
more precise estimate of the association with health risk.

[Env. Epi. book---advantages and disadvantages of different types of measures]

We agree that it is helpful to clarify for readers that these independent
hazards can come together in a storm event at different intensities and at
different time windows. We have added some text on this:

[Added text]

However, we disagree that this should be down as an alternative to calculating
agreement. Epidemiologists need to understand how these exposure measurements
agree to help in planning studies and statistical approaches to interpreting the
resulting data. In this sense, "agreement" is providing a measure similar to
correlation for continuous variables; our choice of agreement with the binary
exposure classifications reflects the more common use of binary classifications
for most tropical cyclone epidemiology to date.

Epidemiological studies might focus on tropical cyclone exposures at two levels.
First, they might wish to focus on a specific hazard. For example, a study might
hypothesize that mold growth following flooding from a tropical storm might
increase risk of respiratory health outcomes in the months after a storm. In
this case, the clear causal pathway recommends a focus on one of the storm
hazards, rather than all storm hazards. However, other storm hazards could
confound the association between flood exposure and respiratory health risk if
the other hazards are ignored *and* if they are associated with both the
exposure of interest (storm-associated flooding) and the health outcome. For
example, if wind exposure assessments are in high agreement with flood exposure
assessments for storms, and if wind affects risk of respiratory outcomes by
causing extensive property damage and creating extreme psychological stress,
which can have repercussions on respiratory health, then the wind hazard could
confound the estimated association between storm-related flood exposure and the
health outcome.

This bias would be higher when the confounder and exposure of interest are more
strongly correlated (for continuous variables) or in higher agreement (for
categorical variables). Conversely, if the exposure and the potential confounder
are, in practice, only weakly associated, then the potential for confounding is
low. The Jaccard index is one measure of similarities between categorical
(including binary) coefficients.

Another consideration is collinearity. If one hazard is the exposure of interest
and another hazard is a potential confounder, then the model should adjust the
confounder or it will be misspecified and be prone to bias. However, if the
exposure of interest and the potential confounder are very strongly
correlated/in agreement, then including both as independent variables in a
regression model often causes numerical problems in fitting the regression
model, including instability in the estimated coefficients and inflated
variance. In very extreme cases, the statistical software may not be able to
invert the matrix [? only for linear regression?].

Therefore, it is helpful for epidemiologists to understand if these independent
storm-associated hazards tend to be strongly associated (in high agreement),
both within specific storms (for single-storm studies) and on average across
most large storms (for multi-storm studies). This knowledge will help them in
identifying potential confounders if they are interested in studying the effects
of a single hazard of the storm and also in determining if control for these
potential confounders among other storm hazards might cause numerical problems
or other collinearity-associated problems when fitting a regression model.

If a researcher wishes to study the storm as a whole, then the researcher 
could either seek a single measure to capture exposure to the storm as a whole
or investigate more complex models that model the influence of the storm through
pathways of several different hazards.

If a researcher wants a single measure for the storm as a whole, then it is
helpful to know how well exposure assessments based on the hazard components of
the storm agree with each other. If there is strong agreement, then any of those
hazards could be used as a primary marker of exposure assessment. This is
conceptually similar to checking for observer / rater agreement.

> "When the row and column variable srepresent different observers' rating the
same subjects or objects, interest is focused on *observer agreement* rather
than mere association. In this case, measures and tests of agreement provide a
method of assessing the reliability of a subjective classification or assessment
procedure." [@friendly2015discrete]

> "In assessing the strength of *agreement* we usually have a more stringent
criterion than in measuring the strength of *association*, because observers
ratings can be strongly associated without strong agreement. For example, one
rater could use a more stringent criterion and thus consistently rate subjects
one category lower (on an ordinal scale) than another rater. More generally,
measures of agreement must take account of the marginal frequencies with which
two raters use the categories. If observers tend to use the categories with
different frequency, this will affect measures of agreement."
[@friendly2015discrete]

When you have an array of two or more exposures that are strongly correlated,
including them together in a regression model can cause problems from
collinearity [@schisterman2017collinearity].

> "Environmental exposures ... often consist of an array of related individual
factors that may be highly correlated with each other, causing concern about the
impact of collinearity when attempting to identify individual effects."
[@schisterman2017collinearity]

**Commonly have multiple factors of interest, correlated**

In some areas of epidemiology, researchers have moved toward the idea of a 
"web of causality":

> "'Multiple causation' is the canon of contemporary epidemiology, and its
metaphor and model is the 'web of causation'. Expressed through the notion
of 'multifactorial etiology' and embedded in the statistical techniques
of 'multivariate analysis', the belief that population patterns of health 
and disease can be explained by a complex web of numerous interconnected 
risk and protective factors has become one of this discipline's central 
concepts. Equally entrenched is the corrolary that epidemiology's power
to improve the public's health rests upon its ability to identify---and predict
the results of breaking---selected strands of this causal web." [@krieger1994epidemiology]

This is in contrast to focusing on single factors:

> "Expressly challenging the still-pervasive tendency of epidemiologists to
think in terms of single 'agents' causing discrete diseases, the provocative
metaphor and model of the 'web' invited epidemiologists to embrace a more
sophisticated view of causality." [@krieger1994epidemiology]

In this framework, epidemiology helps by identifying where it would help to
break strands of the web:

> "Using this model, MacMahon et al. drew several important inferences about
prevention and research that remain part of epidemiologic thinking to this day.
Arguing that 'to effect preventative measures, it is not necessary to understand
causal mechanisms in their entirity', they stated that 'even knowledge of one
small component may allow some degree of prevention' since 'wherever the chain
is broken the disease will be prevented'." [@krieger1994epidemiology]

In other words, if you can identify *necessary* causes, you can craft 
*practical* interventions.

In some fields of epidemiology (e.g., nutritional epidemiology), it is common 
to study cases where there are multiple potential risk factors, and these 
factors are often strongly correlated [@schisterman2017collinearity].

> "The dynamics of many important ecological and evolutionary processes are 
often influenced by multiple interacting factors, and attempting to understand 
the dynamics of such systems presents difficult technical and philosophical 
problems." [@petraitis1996inferring]

> "Often in practice, investigators are faced with decisions of how to handle
highly correlated variables." [@schisterman2017collinearity]

**Methods to tackle multiple causality**

When the aim is to explore the influences of multiple associated factors, there
are some different strategies that can be used. These include multiple
regression and path analysis:

> "Evolutionary ecologists have recently turned to path analysis, multiple
regression, and related techniques to analyse systems of multiple causality.
While these techniques are often seen as competitors, they are, in fact,
related, and as a result the problems of these techniques are similar."
[@petraitis1996inferring]

**Implications of collinearity**

> "Two variables are defined as collinear if one can be expressed as an exact
or near linear combination of the other. ... In general, collinearity between
variables is described by the magnitude of their correlation." 
[@schisterman2017collinearity]

It can complicate inference of model coefficients. This is always a concern for 
inferential models. For predictive models, it can be a problem if you later use
the model to predict in a case where the correlation structure is different than
in the training data.

> "The dependence of regression and path coefficients on the correlation
structure is often glossed over. Yet this dependence means that inferences about
the strengths of path coefficients are conditional upon the correlational
structure among the predictor variables. If the correlation structure of the
sample does not match the correlational structure of the population then
regression and path coefficients will not estimate relative strengths
accurately. This can occur if sampling is not random or if analysis is based on
data from experiments with factorial designs, which break the correlational
structure amnog the predictor variables." [@petraitis1996inferring]

These implications can depend on whether the modeling goal is predictive or 
inferential.

> "When the goal is to choose covariates based on their predictive value, 
concerns about collinearity stem from the desire to improve parameter estimates'
precision, which can be inflated when highly correlated covariates are included
in the model." [@schisterman2017collinearity]

> "In a causal framework, on the other hand, interest is often centered on a
specific effect from a correctly specified causal model, even in the presence of
highly correlated data, despite a potential loss of statistical efficiency.
Under such a viewpoint, bias due to misspecification of the causal associations
is a more devastating result than reduced precision of parameter estimates
correctly estimated. Furthermore, a precisely but incorrectly estimated
parameter may lead to invalid inferences. ... Relying on conventional
variable-selection algorithms and standard analyses can ignore important
confounders and even produce extremely imprecise confidence intervals."
[@schisterman2017collinearity]

The amount of bias in the unadjusted model (in terms of bias from an unadjusted
confounder) depends on the strength of association between the exposure of
interest and the potential confounder [@schisterman2017collinearity].

> "This is especially important for the confounding variable scenario, where 
correctly specifying the model may result in adjusting for a nearly 
collinear variable." [@schisterman2017collinearity]

The degree of agreement will influence the degree of confounding in an 
unadjusted model, for either one or two confounders:

> "In this confounding scenario, increasing correlation exacerbates the bias
due to misspecification, similar to results for a single confounder."
[@schisterman2017collinearity]

Extreme collinearity can create numerical problems
[@schisterman2017collinearity].

> "Under the extremely unlikely scenario of extreme collinearity [(abs. rho of
0.999 or higher)], the numerical matrix inversion required for estimation fails,
resulting in unstable and biased predictors." [@schisterman2017collinearity]

> "Only for extreme values of rho cloes to 1 or -1 is beta-squareed
nonidentifiable due to numerical instability; otherwise, the correctly specified
model produces the most desirable (e.g., unbiased) estimates of the total effect
of the exposure on the outcome." [@schisterman2017collinearity]

Collinearity can cause imprecision in coefficient estimates, even if those
estimates are unbiased [@schisterman2017collinearity].

> "Multicollinearity: A term that refers to correlation among the independent
variables in a multiple regression model; it is usually invoked when some 
correlations are 'large', but an actual magnitude test is not well defined.[1]"
[@gunasekara2008glossary]

> "Collinearity occurs in multiple regression models when two (or
more---multicollinearity) exposure variables are included in the model but are
so similar to each other that they are essentially measuring at least part of
the same thing. Collinearity creates problems with interpreting the analysis by
affecting the standard errors of the variables (as it increases variance)[24]
and by causing biased estimates for one or both of the collinear terms
(sometimes dramatically so) [25]. If there is perfect collinearity between two
variables then one should be dropped from the model. However, dropping exposure
variables to reduce multicollinearity may lead to bias in the model from
dropping useful information." [@gunasekara2008glossary]

> "It might be argued in some cases that it is appropriate to include
(collinear) variables in a model even when they are highly correlated, because
the theoretical basis for including the variables is strong and the results of
the model are consistent with expectations [10]. In such cases, models with and
without the variables would be tested and compared. Such consideraion of
alternative models tends to be described as an issue of (mis)-specification in
econometrics. However, in epidemiology this tends to be described in terms of
mediating and *intermediary variables*. Thus, an epidemiologist might argue for
including an intermediate variable in a model (and testing it against a model
without the variable) because including that variable might elucidate direct and
indirect pathways between the exposure and outcome variables. An econometrician
might do the same thing but describe this in terms of finding the correct model
specification." [@gunasekara2008glossary]

**Techniques to address collinearity**

There are study designs that might help to separate different effects. For
example, some matching designs might help in creating a subset of data in which
the association that exists in the full dataset is broken (e.g.,
@leal2012multicollinearity).

> "Matching is typically employed to reduce model dependence and estimate 
associations in a more empirical way than would be necessary without 
matching. In line with this practice, matching was employed as a diagnostic
tool to verify whether the effects of environmental variables that are highly 
correlated with each other could be disentangled." [@leal2012multicollinearity]

You could also explore techniques of dimension reduction, to create a smaller
subset of independent variables for which the correlation is broken. For
example, you could use PCA [@leal2012multicollinearity].

There are other techniques that allow some bias in estimates in an attempt to
reduce problems from collinearity, like ridge regression
[@petraitis1996inferring].

> "Several biased estimation techniquest ahve been proposed as a way to combat
collinearity (Myers 1990). These are controversial methods. Ridge regression,
for example, biases the regression coefficients in order to improve the model's
ability to predict the criterion variable. The estimates of the individual
regression coefficients may be very biased even though when taken together they
provide a very good prediction of the criterion variable."
[@petraitis1996inferring]

> "When correct specification of the models still leads to 
problems for conventional regression methods, one can apply modern techniques
such as Bayesian hierarchical models with shrinkage estimators."
[@schisterman2017collinearity]

**Are effects of different factors 'separable'?**

Epidemiology often aims to inform policy decisions. In this case, it can be
important to characterize the separate effects of different associated factors
that contribute to the health risk [@leal2012multicollinearity].

> "To develop efficient public health interventions addressing the obesity 
epidemic, it is important to identify exactly which aspects of the
environment influence obesity risk. For example, demonstrating that the density 
of fast-food restaurants was associated with obesity risk and demnstrating that
the density of sports facilities was associated with obesity risk would lead to 
different interventions." [@leal2012multicollinearity]

However, it can be very difficult to separate the effects of different factors
if those factors are strongly correlated [@leal2012multicollinearity]:

> "However, many neighborhood characteristics, especially those related to the
densities of physical features and services, are strongly correlated with each
other. Therefore, it is not clear whether it is even possible to disentangle the
effects of these different environmental dimensions, even if they are
hypothesized to influence obesity risk through distinct causal pathways."
[@leal2012multicollinearity]

-----------------------------------------------------------------------------

As we note in our general response to your comments, we agree in general with
your instinct here. However, there are some subtle points to note.

First, we understand the potential appeal of creating a single exposure summary
score based on a summation of exposures. This simplifies some of the statistical
modeling, for example, and also provides a single exposure estimate to provide
as the key study conclusion. However, in many areas of tropical cyclone
epidemiology, it is unlikely that exposure to each type of hazard should be
given equal weight. For example, an analysis of respiratory health in the months
after the storm might hypothesize a strong connection with flooding, and smaller
connections with rainfall and winds (through the pathway of property damage).
Use of a pre-defined summation of exposure to each hazard would mask some of the
potential association.

While a summary statistic could be defined that adds a weight to each exposure,
it would often be unclear *a priori* what weight each hazard exposure should be
given. A better method might be to use a regression framework, where each hazard
exposure is included as a separate explanatory variable, and the model uses the
observed data to determine the appropriate weight for each hazard in terms of
modifying risk to the outcome of interest. To explore the influence of multiple
concurrent hazards, interaction terms could be added.

However, if our analysis had found that hazard exposures follow very similar
patterns, in terms of the counties exposed during a storm, then this strong
agreement would result in a number of problems in fitting and interpreting these
types of models. First, strong agreement in two or more of the explanatory
variables in a regression model leads to collinearity, which among other
implications often leads to a large inflation of confidence intervals for the
effect estimates of the correlated explanatory variables. Further, if the hazard
exposures were in strong agreement, then it would be difficult or impossible to
disentagle the effects of the separate hazards, as a strong effect for one would
be impossible to interpret with confidence, since the strong agreement in the
data (and resulting low co-variability in the variables in the data) could cause
the model to mistakenly attribute the effect of one hazard to the other.
Further, it may become impossible in this case to estimate synergistic effects
between the two, as an indicator of an interaction between the two exposures
would be almost collinear with the two main effects.

In our analysis, we find that this is usually not the case for the four tropical
cyclone hazards that we consider. Instead, we find that for most storms, the
hazards are fairly well-separated in terms of the counties they effect. There is
a particularly strong pattern where inland counties can be exposed to extreme
rain and flooding, but not wind. This separation opens the door for some
interesting study designs and statistical modeling. For example, these patterns
suggest that a study could investigate whether storm-associated rains alone
create a health risk, as there are many exposures with only rain in inland
counties, and so health associations could be explored here and contrasted with
coastal areas that experienced both wind and extreme rain.

-------------------------------------------------------------------------------

> "A job exposure matrix (JEM) may be defined as a cross classification of jobs
and occupational exposures. Some matrices are based on tasks, instead of jobs. 
... Usually there is a group of experts who build the matrix based on their 
own knowledge and experience on occupational exopsures. The experts should 
assess exposure to an open or fixed list of occupational exposures (that can 
include chemical, physical, biological, and/or psychosocial agents) for an
open or fixed list of jobs (or tasks) usually coded according to some established
national or international classification system. Some JEMs also include 
information for different calendar time periods." [@garcia2003glossary]

[New advances in multi-pollutant analysis.]

[Some of the hazards could create similar risks, if they converge on a common
pathway of risk. For example, if pathway is through stress from property damage,
individually and in the county, then several hazards could indeed lead to the
same health outcomes (e.g., PTSD, other psychological markers, risk of acute
cardiovascular outcomes, etc.). One example is extreme level of destruction both
from wind (Hurricane Andrew, Hurricane Hugo), from river flooding associated
with among of precipitation (Hurricane Floyd, Hurricane Florence), and from
flash flooding associated with the rate of precipitation (Virginia storms).]

[A better future direction might be through regression models with multiple
explanatory pathways. This allows the model to fit different weights to each.
Other models can also be explored, like regression trees, which might have an
easier time capturing non-linearity (if exposure is included as a continuous
value, as with wind and rain) and interactions when there are co-exposures to
two or more hazards. Both of these are able (and will) either exclude or give a
very low weight to an explanatory variable that does not help much in explaining
variation in the health outcome.]
